Syntax and Semantics of Indexed Abstract Binding Trees

### 2015-11-08 paper.tex
cite Ulf's thesis for agda

The contribution of this paper is the development of the syntax and semantics
of \emph{indexed multi-sorted abts}, an extension of second order universal
algebra to support symbol-indexed families of operators. Additionally, we have
developed the categorical semantics for indexed abts formally in Constructive
Type Theory using the Agda proof assistant.

>>>>

The contribution of this paper is the development of the syntax and semantics
of \emph{indexed multi-sorted abts}, an extension of second order universal
algebra to support symbol-indexed families of operators. Additionally, we have
developed the categorical semantics for indexed abts formally in Constructive
Type Theory using the Agda proof assistant \cite{norell:2007}.
